Improving Day Ahead Electricity Load Forecasts with Google Trends

### 2014-07-29 Paper/DraftPaper.Rnw
Most of the tables and figure are in.  I may add one that shows that all the weather searches are significant.

  \subsection{PJM Load Forecasts and Actuals}
<<>>=
HourModelForecastCheck<-function(hour){
  Hour<-formatC(hour, width=2, flag="0")
  as.formula(paste("HE",Hour,"~ F",Hour,sep='' ))}

@@

@@

@@

lapply(1:24, FUN = CompareRaw)
mean(unlist(lapply(1:24, FUN = CompareRaw)))

@@

lapply(1:24, FUN = CompareSigma)
mean(unlist(lapply(1:24, FUN = CompareSigma)))

@@

@@

<<echo=false,results=hide>>=
summary(lm(HE19~F19+NewsTrends,data=WTrends))
# Oh, that works too
summary(lm(HE19~F19+GasTrends,data=WTrends))
# Gas does not
summary(lm(HE19~F19+TrafficTrends,data=WTrends))
# Traffic does not
summary(lm(HE19~F19+RestaurantTrends,data=WTrends))
# Restaurant does not
summary(lm(HE19~F19+MovieTrends,data=WTrends))
# Snort...Movie does.  Cool place to be.
@

@@

>>>>

  \subsection{PJM Load Forecasts and Actuals}

<<echo=false,results=hide>>=
HourModelForecastCheck<-function(hour){
  Hour<-formatC(hour, width=2, flag="0")
  as.formula(paste("HE",Hour,"~ F",Hour,sep='' ))}

@@

\begin{figure}
\begin{center}
\caption{Confidence Intervals for Intercept Statistically Adjusted Models (95\%)}
<<echo=false,fig=TRUE>>=
library(ggplot2)
LowInter<-unlist(lapply(SAResults, FUN= function(x) confint(x) [1,1]))
HighInter<-unlist(lapply(SAResults, FUN= function(x) confint(x) [1,2]))
InterceptResults<-data.frame(1:24,LowInter,HighInter)
names(InterceptResults)[1]<-"Hour"

ggplot(InterceptResults, aes(Hour))+geom_pointrange(aes(y=LowInter, ymin=LowInter,ymax=HighInter))+geom_abline(intercept = 0)+ylab("Intercept Confidence Interval")
@
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\caption{Confidence Intervals for Co-Movement Statistically Adjusted Models (95\%)}
<<echo=false,fig=TRUE>>=
library(ggplot2)
LowInter<-unlist(lapply(SAResults, FUN= function(x) confint(x) [2,1]))
HighInter<-unlist(lapply(SAResults, FUN= function(x) confint(x) [2,2]))
InterceptResults<-data.frame(1:24,LowInter,HighInter)
names(InterceptResults)[1]<-"Hour"

ggplot(InterceptResults, aes(Hour))+geom_pointrange(aes(y=LowInter, ymin=LowInter,ymax=HighInter))+geom_abline(intercept = 1,slope=0)+ylab("Intercept Confidence Interval")
@
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\caption{State Weather Trends Indexes Over Time}
<<echo=false,fig=TRUE>>=
library(ggplot2)
library(reshape2)

JustWeather<-data.frame(WTrends$Date, WTrends$DETrends,WTrends$KYTrends, WTrends$MDTrends, WTrends$NJTrends, WTrends$OHTrends, WTrends$PATrends, WTrends$VATrends, WTrends$WVTrends, WTrends$Weather)

names(JustWeather)<-c("Date","DE","KY","MD","NJ","OH","PA","VA","WV","Weather")

MeltedTrends<-melt(JustWeather,variable.name="Index",id.var="Date",na.rm=TRUE)

ggplot(MeltedTrends, aes(Date, value,group= Index))+geom_line() +ylab("Index")+facet_grid(Index~.)

@
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\caption{Trends Indexes Over Time}
<<echo=false,fig=TRUE>>=
library(ggplot2)
library(reshape2)

JustTrends<-data.frame(WTrends$Date, WTrends$GasTrends,WTrends$MovieTrends, WTrends$NewsTrends, WTrends$RestaurantTrends, WTrends$TrafficTrends,WTrends$Weather)
names(JustTrends)<-c("Date","Gas","Movie","News","Restaurant","Traffic","Weather")

MeltedTrends<-melt(JustTrends,variable.name="Index",id.var="Date",na.rm=TRUE)

ggplot(MeltedTrends, aes(Date, value,group= Index))+geom_line() +ylab("Index")+facet_grid(Index~.)

@
\end{center}
\end{figure}

@@

DirectCompare<-lapply(1:24, FUN = CompareRaw)
mean(unlist(lapply(1:24, FUN = CompareRaw)))

@@

ModelCompare<-lapply(1:24, FUN = CompareSigma)
mean(unlist(lapply(1:24, FUN = CompareSigma)))

@@

<<echo=FALSE,results=tex>>=
ForCompareTable<-data.frame(1:24,unlist(DirectCompare)*100,unlist(ModelCompare)*100,unlist(CVImprove)*100)
names(ForCompareTable)<-c("Hour","Direct","Statistically Adjusted (Raw)", "Statistically Adjusted (CV)")
library(stargazer)
stargazer(ForCompareTable,summary=FALSE, title="Improvement in Forecasts Relative to Gross,  Statistically Adjusted, Drop Forward CV (Percent)",rownames=FALSE)
@

@@

<<echo=false,results=tex>>=
News<-lm(HE19~F19+NewsTrends,data=WTrends)
# Oh, that works too
Gas<-lm(HE19~F19+GasTrends,data=WTrends)
# Gas does not
Traffic<-lm(HE19~F19+TrafficTrends,data=WTrends)
# Traffic does not
Restaurant<-lm(HE19~F19+RestaurantTrends,data=WTrends)
# Restaurant does not
Movie<-lm(HE19~F19+MovieTrends,data=WTrends)
# Snort...Movie does.  Cool place to be.
library(stargazer)
stargazer(News,Gas,Traffic,Restaurant,Movie,title="Alternate Google Search Models for Hour 19",column.labels=c("News","Gas","Traffic","Restaurant","Movie"), dep.var.caption="Hour 19 Load",dep.var.labels.include = FALSE)
@

@@

\appendix

\section{Hourly Models with Weather Searches}

<<echo=false,results=tex>>=

for(x in 1:12){
  stargazer(GrossTrends[[x]], title=paste("Hour",x), dep.var.labels=paste("Hour",x), covariate.labels=c("Forecast","Weather","Constant") )
}
@
\clearpage

<<echo=false, results=tex>>=

for(x in 13:24){
  stargazer(GrossTrends[[x]], title=paste("Hour",x), dep.var.labels=paste("Hour",x), covariate.labels=c("Forecast","Weather","Constant") )
}
@
